Impact of cosmic variance on the galaxy-halo connection for Lyman-$\alpha$ emitters

### 2016-06-14 paper/ms.tex
new title, new acknowledgemets

\begin{document}
%=========================================================================
%		FRONT MATTER
%=========================================================================
\title{Uncertainty on the galaxy-halo connection for Lyman-$\alpha$ emitters at $z=3.1$}
\author{
  Juli\'an E. Mej\'ia-Restrepo \thanks{jemejia@das.uchile.cl}$^{1,3}$,
  Jaime E. Forero-Romero \thanks{je.forero@uniandes.edu.co}$^{2}$ 
}

@@

The authors acknowldge the referee, Nelson Padilla, for useful
remarks and questions that helped us to improve the quality and
clarity of our paper.

>>>>

\begin{document}
%=========================================================================
%		FRONT MATTER
%=========================================================================
\title{Impact of cosmic variance on the galaxy-halo connection for Lyman-$\alpha$ emitters }
\author{
  Juli\'an E. Mej\'ia-Restrepo \thanks{jemejia@das.uchile.cl}$^{1,3}$,
  Jaime E. Forero-Romero \thanks{je.forero@uniandes.edu.co}$^{2}$ 
}

@@

The authors acknowldge the referee, Nelson Padilla, for useful
remarks and questions that helped us to improve the quality and
clarity of our paper. The authors also acknowldge Valentino Gonzalez,
Eric Gawiser and Mark Dijkstra for the fruitful discussion and
suggestions that also contributed to improve the quality of this work.
